Cudele: Programmable Consistency and Fault Tolerance

### 2017-03-18 paper/sections/4_methodology.tex
paper: add hotstorage draft
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{table}[t]
\begin{center}
\caption{Future programmers can explore the consistency (C) and
durability (D) spectrums by composing Cudele mechanisms. The consistency
and durability properties are not guaranteed until all mechanisms in the cell
are complete (i.e. the compositions should be considered atomic) and there are
no guarantees while tranisitioning between policies. \label{table:spectrum}}
\begin{tabular}{ l | l | l | l }
  C \(\rightarrow\) &&& \\  
  D \(\downarrow\)  & none              & eventual        & strong  \\\hline
  none                       & create            & create          & RPCs    \\
                             &                   & +volatile apply &         \\\hdashline
  local                      & create            & create          & RPCs    \\
                             & +local persist    & +local persist  & +local persist \\
                             &                   & +volatile apply &         \\\hdashline
  global                     & create            & create          & RPCs    \\
                             & +global persist   & +global persist & +stream \\
                             &                   & +volatile apply &         \\
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Cudele Namespace API: Per-Subtree Policies}

@@

>>>>

\begin{table}[t]
\begin{center}
\caption{Future programmers can explore the consistency (C) and
durability (D) spectrums by composing Cudele mechanisms. The consistency
and durability properties are not guaranteed until all mechanisms in the cell
are complete (i.e. the compositions should be considered atomic) and there are
no guarantees while tranisitioning between policies. \label{table:spectrum}}
\begin{tabular}{ l | l | l | l }
  Consistency \(\rightarrow\) &&& \\  
  Durability \(\downarrow\)  & invisible         & eventual        & strong  \\\hline
  none                       & create            & create          & RPCs    \\
                             &                   & +volatile apply &         \\\hdashline
  local                      & create            & create          & RPCs    \\
                             & +local persist    & +local persist  & +local  \\
                             &                   & +volatile apply &  persist\\\hdashline
  global                     & create            & create          & RPCs    \\
                             & +global persist   & +global persist & +stream \\
                             &                   & +volatile apply &         \\
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Cudele Namespace API:\\Per-Subtree Policies}

@@

\begin{listing}
\begin{minted}[frame=single,
               framesep=3mm,
               xleftmargin=21pt,
               tabsize=4]{js}
{     
    "allocated_inodes": "100000"
    "interfere_policy": "block"
    "consistency": "create"
    "durability": "local_persist"
}
\end{minted}
\caption{Implementing DeltaFS with Cudele.}
\label{src:deltafs}
\end{listing}

\begin{listing}
\begin{minted}[frame=single,
               framesep=3mm,
               xleftmargin=21pt,
               tabsize=4]{js}
{     
    "allocated_inodes": "100000"
    "interfere_policy": "block"
    "consistency": "create+volatile_apply"
    "durability": "local_persist"
}
\end{minted}
\caption{Implementing BatchFS with Cudele.}
\label{src:batchfs}
\end{listing}

\begin{listing}
\begin{minted}[frame=single,
               framesep=3mm,
               xleftmargin=21pt,
               tabsize=4]{js}
{     
    "allocated_inodes": "-"
    "interfere_policy": "-"
    "consistency": "RPCs"
    "durability": "stream"
}
\end{minted}
\caption{Existing CephFS on Cudele.}
\label{src:batchfs}
\end{listing}
